Living on the edge: crop boundary effects on canola and wheat yields in Alberta

### 2021-09-01 Manuscript/manuscript.Rmd
Added example section with single field

datSource <- read.csv('../Data/datSource.csv') #Get data source
datSourceFinal <- datSource %>% filter(use) %>% filter(grepl('Wheat|Canola',crop))
yearsPerField <- datSourceFinal %>% count(field) %>% pull(n) #How many years of data at each unique location?

@@

## Field boundaries

@@

## Canola

There was a strong negative effect combine ground speed on both the average and variability of canola yield.
At the field level, both yield average and yield variability (SD of yield) of yield were extremely spatially (average p-values: `r canolaMods$meanP[canolaMods$Smoother=='s(E,N)']`, `r canolaMods$meanP[canolaMods$Smoother=='s.1(E,N)']`) and temporally dependent (`r canolaMods$meanP[canolaMods$Smoother=='s(r)']`, `r canolaMods$meanP[canolaMods$Smoother=='s.1(r)']`), meaning that average and variablity changed with location in the field, as well as sequentially during the harvest.
However, there was no difference in average or variability with harvest sequence when all fields were considered, meaning that combines did not appear to distort yield data from start to finish in any systematic way.

@@

## Wheat

>>>>

source('../helperFunctions.R')

datSource <- read.csv('../Data/datSource.csv') %>% #Get data source
    mutate(modelComplete2=file.exists(paste0('.',modelPath2)))  #Has model2 already been run?

datSourceFinal <- datSource %>% filter(use) %>% filter(grepl('Wheat|Canola',crop)) 
yearsPerField <- datSourceFinal %>% count(field) %>% pull(n) #How many years of data at each unique location?

@@

## Field-level exanoke

The filtered data from each field still contained a large amount of variation, but the non-stationary additive models were able to reveal underlying yield patterns.
Figure \@ref(fig:examplePlot1)b shows the results from a single field to illustrate this, where areas of higher yield are clearly visible within the field.
Additionally, Figure \@ref(fig:examplePlot1)c shows that yield "patchiness" (standard deviation, SD) also varies within fields, with areas of higher and lower patchiness also clearly visible within fields.

```{r examplePlot1, echo=FALSE, fig.cap='Example output from a single field.', out.width='100%'}  
  include_graphics('../Figures/ExamplePlots/Trent_Clark JOHNSON 2014.png',dpi=NA)
```
```{r examplePlot1, echo=FALSE, fig.cap='Distance smoothers from a single field.', out.width='100%'}  
  include_graphics('../Figures/ExamplePlots/Trent_Clark JOHNSON 2014 Summary.png',dpi=NA)
```

## All canola fields

@@

There was a strong negative effect combine ground speed on both the average and variability of canola yield.
At the field level, both yield average and yield variability (SD of yield) of yield were extremely spatially (average p-values: `r with(canolaMods,formatC(meanP[Smoother=='s(E,N)']))`, `r with(canolaMods,formatC(meanP[Smoother=='s.1(E,N)'],3))`) and temporally dependent (`r with(canolaMods,formatC(meanP[Smoother=='s(r)'],3))`, `r with(canolaMods,formatC(meanP[Smoother=='s.1(r)'],3))`), meaning that average and variability changed with location in the field, as well as sequentially during the harvest.
However, there was no difference in average or variability with harvest sequence when all fields were considered, meaning that combines did not appear to distort yield data from start to finish in any systematic way.

@@

## All wheat fields

### 2021-09-01 Manuscript/supplemental.Rmd
Added example section with single field

Supplemental materials here

>>>>

```{r , echo=FALSE, fig.cap='Effect of ground speed and order (sequence of harvest) on canola yield.', out.width='100%'}  
  include_graphics('../Figures/groundSpeed_canola.png',dpi=NA)
```

```{r , echo=FALSE, fig.cap='Effect of ground speed and order (sequence of harvest) on wheat yield.', out.width='100%'}  
  include_graphics('../Figures/groundSpeed_wheat.png',dpi=NA)
```
